---
title: "Writing reports with R markdown"
author: "Jun Kit"
date: "2022-10-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999) # to prevent scientific notation of digits, ie 4.12321{10}
```

```{r packages, include=FALSE}
library(tidyverse)
library(here)
library(knitr)
```

This report was prepared for the UN. It analyzes the relationship between a country's GDP, life expectancy, and CO2 emissions. Our goal was to determine to what degree a country's economic strength or weakness may be related to its public health and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions will increase with a country's GDP.

```{r data, include=FALSE}
gapminder_1997 <- read_csv(here("data/gapminder_1997.csv"),show_col_types = FALSE)
```

```{r gdp_life_exp_1997, echo = FALSE}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp, color = continent, 
                           size = pop/1000000))+
  geom_point()+
  labs(x = "GDP per Capita",
       y = "Life Expectancy",
       title = "Do people in wealthy countries live longer?",
       size = "Population (in millions)",
       color = "Continent")
```
```{r summary_data, include = FALSE}
n_countries <- gapminder_1997 %>%
  select(country)%>%
  n_distinct()

min_gdp <- gapminder_1997 %>%
  summarize(round(min(gdpPercap)))

max_gdp <- gapminder_1997 %>%
  summarize(round(max(gdpPercap)))
```

The above plot shows the relationship between GDP per capita and life expectancy for a total of `r n_countries` countries. For this set of countries, economic wealth ranged from a minimum of $`r min_gdp` to a maximum of $`r max_gdp` per capita

| Summary of Data |
|--------|--------|
| Number of countries | `r n_countries` |
| Minimum GDP per cap | `r min_gdp` |
| maximum GDP per cap | `r max_gdp` |


```{r tables, echo = FALSE}
gapminder_1997 %>%
  filter(continent == "Oceania")%>%
  select(-continent)%>%
  kable(col.names = c("Country","Population","Life Expectancy","GDP per Capita"))
```
## Lists

### Unordered
- Favorite programming language: **Python**
- Most useful function: *read_csv()*
- Next steps: ***Learn C++***

### Ordered
1. Favorite programming language: **Python**
    + C++ comes 2nd
2. Most useful function: *read_csv()*
3. Next steps: ***Learn C++***
4. Useful Markdown Reference: [Markdown Cheat Sheet]( https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)





